An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-22 scagnostics.Rmd
Added title/values to Fig. 17

iLast <- length(bbhTourFull12)
fProj1 <- bbhTourFull12[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj1)
colnames(fProj1) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj1 <- as_tibble(fProj1) %>%
  add_column(label=colnames(bbhM2))
p1 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(1, 0, 0.34, 0.25), aes(x=x, y=y), color="grey") + 
  xlim(-0.2, 1.5) + ylim(-0.25, 1) +
  geom_segment(data=getAxes(fProj1,1, 0, 0.34, 0.25), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj1, 1, 0, 0.34, 0.25), aes(x=x2, y=y2, label=label), size=2.5)
iLast <- length(bbhTourFull22)
fProj2 <- bbhTourFull22[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj2)
colnames(fProj2) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj2 <- as_tibble(fProj2) %>%
  add_column(label=colnames(bbhM2))
p2 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0.75, 0, 0.25, 0.24), aes(x=x, y=y), color="grey") + 
  xlim(-0.25, 1) + ylim(-0.9, 0.3) +
  geom_segment(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x2, y=y2, label=label), size=2.5)
iLast <- length(bbhTourFull32)
fProj3 <- bbhTourFull32[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj3)
colnames(fProj3) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj3 <- as_tibble(fProj3) %>%
  add_column(label=colnames(bbhM2))
p3 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0, 1.25, 0.32, 0.32), aes(x=x, y=y), color="grey") + 
  xlim(-0.4, 1.2) + ylim(0, 1.6) +
  geom_segment(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x2, y=y2, label=label), size=2.5)
grid.arrange(p1, p2, p3, ncol=3) 
```

>>>>

iLast <- length(bbhTourFull12)
fProj1 <- bbhTourFull12[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj1)
colnames(fProj1) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj1 <- as_tibble(fProj1) %>%
  add_column(label=colnames(bbhM2))
iv <- mine(dProj$PP1,dProj$PP2)["TIC"]
p1 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1) + 
  geom_path(data=getCircle(1, 0, 0.34, 0.25), aes(x=x, y=y), color="grey") + 
  xlim(-0.2, 1.5) + ylim(-0.25, 1) +
  geom_segment(data=getAxes(fProj1,1, 0, 0.34, 0.25), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj1, 1, 0, 0.34, 0.25), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("a, TIC: ", toString(format(iv, digits=2))))
iLast <- length(bbhTourFull22)
fProj2 <- bbhTourFull22[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj2)
colnames(fProj2) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj2 <- as_tibble(fProj2) %>%
  add_column(label=colnames(bbhM2))
iv <- splines2d(dProj$PP1,dProj$PP2)
p2 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0.75, 0, 0.25, 0.24), aes(x=x, y=y), color="grey") + 
  xlim(-0.25, 1) + ylim(-0.9, 0.3) +
  geom_segment(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj2, 0.75, 0, 0.25, 0.24), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("b, splines2D: ", toString(format(iv, digits=2))))
iLast <- length(bbhTourFull32)
fProj3 <- bbhTourFull32[[iLast]]
dProj <- as.tibble(bbhM2 %*% fProj3)
colnames(fProj3) <- c("PP1", "PP2")
colnames(dProj) <- c("PP1", "PP2")
fProj3 <- as_tibble(fProj3) %>%
  add_column(label=colnames(bbhM2))
iv <- 1-scagnostics(as.matrix(dProj))[,"Convex"]
p3 <- ggplot(dProj, aes(PP1,PP2)) + geom_point(alpha = 0.02) + theme(aspect.ratio=1)+ 
  geom_path(data=getCircle(0, 1.25, 0.32, 0.32), aes(x=x, y=y), color="grey") + 
  xlim(-0.4, 1.2) + ylim(0, 1.6) +
  geom_segment(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x1, xend=x2, y=y1, yend=y2)) +
  geom_text(data=getAxes(fProj3, 0, 1.25, 0.32, 0.32), aes(x=x2, y=y2, label=label), size=2.5) +
  ggtitle(paste0("c, 1-convex: ", toString(format(iv, digits=2))))
grid.arrange(p1, p2, p3, ncol=3) 
```
